Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-01-13 Paper/Paper.tex

It is reasonable to believe that physicians are fully utilizing the EHRs in the hospital they work in, since by 2015 electronic health records were widely implemented and considered unavoidable. An objection to this assumption may be that older physicians stay in a hospital, but the hospital hires a data assistant to do technology work for the physician. In this cae, the productivity gain could be from having the data assistant instead of EHR use. I investigate this below.

@@

\textcolor{red}{get data from AHA on data assistance. It may be that I just need to show a graph here of the number of data assistant jobs at hospitals. Need to see from there. }

@@

>>>>

It is reasonable to believe that physicians are fully utilizing the EHRs in the hospital they work in, since by 2015 electronic health records were widely implemented and considered unavoidable. An objection to this assumption may be that older physicians stay in a hospital, but the hospital hires a data assistant to do technology work for the physician. In this case, the productivity gain could be from having the data assistant instead of EHR use. I investigate this below.

@@

One concern with this measure of productivity is that an increase in the number of patients seen by a physician could be caused by an outside factor that is also correlated with EHR adoption in hospitals. A logical outside factor could be the existence of employees with the purpose of utilizing electronic health records on a physician's behalf. Employees of this type are assigned a medical tax ID when working in hospitals; they have the following titles: Coding Specialist (Hospital Based), Health Information Technologist and Registered Record Administrator. All of these employees are the equivalent of transcribers for health information technology.

Using NPPES data on all NPIs and their tax information, I analyze the existence of data assistants in hospitals. Figure \textcolor{red}{number} is a frequency plot of the year of activation for every tax code that falls in the categories listed above. The total number of these registered employees is 875.

@@

\renewcommand*{\bibfont}{\footnotesize}

\printbibliography

\newpage

\appendix

\section{Tables and Figures}

\begin{table}[ht]
\import{Table Code}{split stats.tex}
\end{table}
